A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-04-12 docs/methods/erosion_methods.tex
NM

\paragraph{Limitations}
We make two fundamental design choices in our simulation: first, we restrict attention to two spatial dimensions, and second the bodies are considered immobile (i.e.~fixed to their initial locations). The restriction to two dimensions allows us to simulate the erosion of many bodies (up to $50$ in this manuscript) with high resolution, enabling accurate characterization of porous-medium erosion. While BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated and makes porous-medium simulations less feasible. Second, the assumption of immobile bodies affords a simple framework to analyze the effects of erosion in isolation. While other mechanisms, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically. We therefore defer to future work the incorporation of these additional mechanisms.

\paragraph{Related Work}
In a closely related study, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions~\cite{mit-spa2016}. The flexibility of their formulation enabled simulations of a {\em mobile} body eroding in an {\em aribtrary} background flow (e.g.~uniform flow, shear flow, etc.).  An advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces.  In the present work, we aim to simulate the erosion of a porous medium and, further, choose to fix the bodies to their initial locations. Thus, rather than a {\em single, mobile} body as considered in~\cite{mit-spa2016}, we aim to simulate the erosion of {\em many, immobile} bodies. Although the traction formulation has several attractive features, we instead employ a standard double-layer formulation since it allows us to easily calculate bulk quantities (e.g.~vorticity, pressure, and velocity) that will assist our understanding of the erosion process.

>>>>

\paragraph{Limitations}
We make two fundamental design choices in our simulation: first, we restrict attention to two spatial dimensions, and second the bodies are considered immobile (i.e.~fixed to their initial locations). The restriction to two dimensions allows us to simulate the erosion of many bodies (up to $50$ in this manuscript) with high resolution, enabling accurate characterization of porous-medium erosion. While BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated and makes porous-medium simulations less feasible. Second, the assumption of immobile bodies affords a simple framework to analyze the effects of erosion in isolation. While other mechanisms, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically. We therefore defer the incorporation of these mechanisms to future work.

\paragraph{Related Work}
In a closely related study, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions~\cite{mit-spa2016}. The flexibility of this formulation enabled simulations of a {\em mobile} body eroding in an {\em aribtrary} background flow (e.g.~uniform flow, shear flow, etc.).  An advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces.  In the present work, we aim to simulate the erosion of a porous medium and, further, choose to fix the bodies to their initial locations. Thus, rather than a {\em single, mobile} body as considered in~\cite{mit-spa2016}, we aim to simulate the erosion of {\em many, immobile} bodies. Although the traction formulation has several attractive features, we instead employ a standard double-layer formulation since it allows us to easily calculate bulk quantities (e.g.~vorticity, pressure, and velocity) that will assist our understanding of the erosion process.
